---
title: "portfolio 6"
output: html_document
date: "2023-04-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
library(readxl)

library(ggplot2)

df <- read_excel("/Users/lindsaystall/Downloads/PIRUS_Public_May2020.xlsx")

df[df == -99 | df == -88] <- NA

```

```{r}
count <- sum(df$Changing_Target == 1, na.rm = TRUE)

cat("Number of times Changing_Target had a value of 1:", count)
```

Now I know that in this dataset, there were 129 instances of terrorists changing their targets over time. I want to figure out what groups these people belonged to.

```{r}
df_filtered <- df[df$Changing_Target == 1,]

group_names <- unique(df_filtered$Terrorist_Group_Name1)

cat("Terrorist_Group_Names with Members who changed their targets:", paste(group_names, collapse = ", "))
```

```{r}
sort(unique(df_filtered$Terrorist_Group_Name1))
```

The top 10 terrorist groups where people change targets are: 
 [1] "al-Qaeda core"                                         
 [2] "Al-Qaeda in Iraq"                                      
 [3] "al-Qaeda in the Arabian Peninsula (AQAP)"              
 [4] "al-Shabaab"                                            
 [5] "Alaska Peacemakers Militia"                            
 [6] "Animal Liberation Front (ALF)"                         
 [7] "Armed Forces of National Liberation (FALN)"            
 [8] "Armed Revolutionary Independence Movement (MIRA)"      
 [9] "Army of God"                                           
[10] "Aryan Nations"   

That said, the codebook for this data doesnt specify the direction of this movement (did they start in this group or end in this group?)

```{r}
count <- sum(df$Anticp_Fatals_Targ == 1, na.rm = TRUE)

cat("Number of times Anticipated_Fatalities_Target had a value of 1:", count)
```

Most (491) terrorist plots in this dataset anticipated to kill some victims, which was about 1-20 

```{r}
count <- sum(df$Anticp_Fatals_Targ == 2, na.rm = TRUE)

cat("Number of times Anticipated_Fatalities_Target had a value of 1:", count)
```


```{r}
count <- sum(df$Anticp_Fatals_Targ == 3, na.rm = TRUE)

cat("Number of times Anticipated_Fatalities_Target had a value of 1:", count)
```

Terrorist plots in this dataset anticipated to kill many victims (over 20) (106) or a mass amount of victims (over 100) (101) were about equal in number.

```{r}
pie_data <- df %>% 
  filter(Anticp_Fatals_Targ %in% c(1,2,3)) %>% 
  group_by(Anticp_Fatals_Targ) %>% 
  summarise(n = n())

ggplot(pie_data, aes(x="", y=n, fill=factor(Anticp_Fatals_Targ))) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  scale_fill_manual(values = c("#0072B2", "#009E73", "#D55E00"),
                    labels = c("Some (< 20)", "Many (> 20)", "Mass (> 100)")) +
  labs(title="Distribution of Anticipated Fatalities in Terrorism Attacks",
       fill="Response",
       x=NULL,
       y=NULL) +
  theme_void()
```

